R for Clinical Study Reports and Submission

### 2021-11-03 tlf-ae-spec.Rmd
Minor syntax fix

More discussion on `page_by`, `group_by` and `subline_by`
features can be found in the
[`r2rtf` package website](https://merck.github.io/r2rtf/articles/example-sublineby-pageby-groupby.html.

>>>>

More discussion on `page_by`, `group_by` and `subline_by`
features can be found in the
[`r2rtf` package website](https://merck.github.io/r2rtf/articles/example-sublineby-pageby-groupby.html).
